---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mscopendata

<!-- badges: start -->
<!-- badges: end -->

The goal of `{{mscopendata}}` is to provide an interface for accessing [Meteorological Service of Canada (MSC) Open Data](https://eccc-msc.github.io/open-data/readme_en/).


## Available Open Data

The available open data from the
[MSC](https://eccc-msc.github.io/open-data/msc-data/readme_en/) provides
up-to-date information on past, present and future weather, water, climate
and environmental conditions over Canada and the world. The main categories
of data available are:

  + Weather alerts, current conditions and public forecasts
  
  + Weather, water and environmental observations and forecast data
  
  + Climate data


## Data Access

The available open data services are:

```{r msc-data-services, echo = F}
msc_services <- tibble::tibble(
  Service = c(
    "[**MSC GeoMet**](https://eccc-msc.github.io/open-data/msc-geomet/readme_en/)",
    "[**MSC Datamart**](https://eccc-msc.github.io/open-data/msc-datamart/readme_en/)"
  ),
  Description = c(
    "<ul>
    <li>Public access to MSC and Environment and Climate Change Canada (ECCC) data</li>
    <li>Access real-time and archived weather, climate and water datasets and products via web services and APIs</li>
    <li>GeoMet platform consists of the following services:</li>
    <ul>
    <li>GeoMet-OGC-API:</li>
    <ul>
    <li>Weather, climate and hydrometric data</li>
    <li>Standards supported: OGC API - Features, OGC API - Processes, STAC (experimental)</li>
    </ul>
    <li>GeoMet-Weather:</li>
    <ul>
    <li>Numerical Weather Prediction systems, weather radar, current conditions, alerts, and more</li>
    <li>Standards supported: WMS, WCS, SLD</li>
    </ul>
    <li>GeoMet-Climate:</li>
    <ul>
    <li>Climate data archives, simulations and scenarios</li>
    <li>Standards supported: WMS, WCS, SLD</li>
    </ul>
    <li>GeoMet-Beta:</li>
    <ul>
    <li>Unsupported web services for experimental data</li>
    </ul>
    </ul>
    </ul>",
    "<ul>
    <li>HTTPS raw data server</li>
    <li>Source of raw weather, water, climate and environmental data</li>
    <li>Location: [https://dd.weather.gc.ca/](https://dd.weather.gc.ca/)</li>
    <li>Data formats: RHIB2, NetCDF, GeoJSON, shapefile, CSV, XML</li>
    </ul>"
  )
)

msc_services |> 
  kableExtra::kbl(
  caption = "Meteorological Service of Canada (MSC) Open Data Services",
  escape = F, 
  booktabs = TRUE,
  align = c('l', 'l')
  ) |> 
  kableExtra::kable_styling(c("hover", "condensed"))
```
